---
name: Georgia
surname: Clay
position: "PhD Candidate"
address: "Institute of Work, Organisational and Social Psychology, Technical University Dresden"
phone: +43670 608 4487
email: "georgia.clay@tu-dresden.de"
github: georgiaclay
date: "`r format(Sys.time(), '%B %Y')`"
profilepic: "picture.jpg"
fontsize: 10pt
headcolor: "414141"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(gsheet)

#install.packages("rorcid")
#install.packages("usethis")
```

# Education 

```{r education}
gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1AL-rCEwDCLcuSC4_5eBoENKnfXpH7cjDSbAXlJ3Rc_o/edit#gid=0", sheet="Education") %>%
  vitae::detailed_entries(what = Degree,
                          when = Year,
                          where = Location, 
                          with = Institution, 
                          why = Details)
```
# Teaching

```{r teaching}
gsheet::gsheet2tbl("https://docs.google.com/spreadsheets/d/1AL-rCEwDCLcuSC4_5eBoENKnfXpH7cjDSbAXlJ3Rc_o/edit#gid=1629311588", sheet="Teaching") %>%
  vitae::detailed_entries(with = Course,
                          when = Year,
                          what = Institution,
                          why = Details)
```

# Publications

```{r publications}
scholar::get_publications('x9BUWucAAAAJ&hl')  %>%
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), year, key = row_number()) %>%
  RefManageR::as.BibEntry() %>% 
  RefManageR::WriteBib("clay.bib")
bibliography_entries("clay.bib") %>%
  arrange(factor(id, levels = c(3,4,2,1)))
```

# Talks and Presentations

```{r}
tribble(
  ~ Talk, ~ Year,
  "\\textbf{Clinical Social Neuroscience Unit, University of Vienna (invited talk)}", "Feb 2022",
  "\\textbf{Department of Psychology, McGill University (invited talk)}",
  "Mar 2022",
  "\\textbf{Mental Effort Workshop (poster presentation)}", "Sep 2021",
  "\\textbf{General Psychology, Friedrich-Schiller-Universität Jena (talk)}",
  "Oct 2020"
) %>%
  brief_entries(what = Talk,
                when = Year,
                .protect = FALSE)
```

# Other skills and achievements

## Courses

```{r}
tribble(
  ~ Course, ~ Date, ~ Details,
  "Summer School on Statistical Methods for Linguistics and Psychology", "Sep 2022", "Week long workshop on multi-level modeling in R",
  "Introduction to Bayesian Data Analysis", "Jan 2023", "Four week online course on Bayesian methods including implementation in R",
  "Google Data Analytics Professional Certificate", "Jun 2022", "Data cleaning, analysing and sharing using SQL, Tableau and R",
  "Summer School on Advanced Regression Analyses", "Jul 2022", "Organised and partook in week long workshop for students of universities in Vienna and Budapest",
  "Junior Researcher Programme", "Jun 2019 - Aug 2020", "Year long research project on willpower beliefs and effort culminating in a Registered Report published in EJPA"
) %>%
 brief_entries(glue::glue("\\textbf{<Course>} \\newline <Details>", .open = "<", .close =">"), paste0(Date, "\\newline"), .protect = FALSE)
```

## Other skills


\begin{itemize}
\item Supervised Masters and Bachelors thesis projects at University of Vienna
\item Highly proficient in R, building experiments using Inquisit (Experiment builder), running studies on Amazon Mechanical Turk and Prolific, experience with Python, MATLAB, MPlus
\item Languages: English (Native) and German (C1)
\end {itemize}

